### 2015-12-14 paper/main.tex
update paper to detail convex optimization

We introduce a novel Empirical Bayes approach for performing large-scale hypothesis testing, including  
estimating False Discovery Rates (FDRs), and estimating effect sizes. Compared with
existing commonly-used approaches to FDR analysis, the method has two key differences. First, it
assumes that the distribution of the actual (unobserved) effects being tested is unimodal, with a mode at 0.
This ``unimodal assumption" (UA), which is common in other related contexts, but very different from assumptions usually made
in FDR analyses, yields more accurate estimates of FDR than existing methods, provided the UA holds.
Second, the method takes as it input two numbers for each test (an effect size estimate, and corresponding standard error),
rather than the one number usually used ($p$ value, or $z$ score). Provided these two numbers are available,
using them allows our method to better account for
variations in measurement precision across tests. It also facilitates the estimation of actual 
effect sizes, and our approach provides ``shrunken" interval estimates (credible regions) for each effect in addition to measures of ``significance".
To provide a bridge between interval estimates and signicance measures we introduce the term ``local false sign rate"
to refer to the probability of getting the sign of an effect wrong, and argue that it is a superior
measure of significance than the local FDR because it is both more generally applicable, and
can be more robustly estimated. Our methods are implemented in an R package {\tt ashr}
available from \url{http://github.com/stephens999/ashr}.

@@

In addition to these two new ideas, we highlight a third idea that is old, but which remains under-used in practice:
the idea that it may be preferable to focus on estimation rather than on testing.
In principle, Bayesian approaches can naturally unify testing and estimation into a single framework -- testing is
simply estimation with some positive prior probability that the effect is exactly zero.
However, despite ongoing interest in this area from both frequentist \cite{benjamini2005false} and Bayesian \cite{zhao2012empirical,gelman2012we} 
perspectives, in practice large-scale studies that assess many effects almost invariably focus on testing significance and
controlling the FDR, and not on estimation. To help provide a bridge between FDR and estimation we introduce the term
``local false sign rate" (lfsr), which is analogous to the ``local false discovery rate" (\lfdr) \cite{efron2008microarrays}, but which measures confidence  
in the {\it sign} of each effect rather than confidence in each effect being non-zero. We show that in some settings, particularly those with many discoveries, 
the $\lfsr$ and $\lfdr$ can be quite different, and emphasise benefits of the $\lfsr$, particularly its increased robustness to modelling assumptions.

@@

Our methods are implemented in an R package, \ashr (for {\bf a}daptive {\bf sh}rinkage in {\bf R}), available at \url{http://github.com/stephens999/ashr}.
(The names comes from the fact that EB methods in general, and -- due to the UA -- our EB method in particular, is a form of shrinkage estimation,
and the shrinkage is adaptive to both the amount of signal in the data and the measurement precision of each observation. 
This will be discussed further in Xing and Stephens (in preparation).)

@@

% Here we consider one setting in which FDR-based methods are widely used:
%an experimenter has measured a large numbers of ``effects", each with an associated
%measurement precision (standard error), 
%and the goal is to identify which of the effects we can declare to be non-zero, with some prescribed level of confidence.
%Although the usual focus of FDR-based methods is on distinguishing zero and non-zero effects,
%here we also focus on providing estimates -- both point estimates and interval estimates -- for these effects.
%This setting arises commonly in many areas of statistics, and particularly in genomics applications.
%For example, in genomics
%a common goal is to identify ``differentially-expressed genes" -- that is, genes
%whose mean expression (activity) level differs in two conditions. Here the ``effect" of interest is the difference in (log) 
%mean expression level between the two conditions, often referred to as the ``log-fold change". 
Here we describe the simplest version of our method, and briefly discuss embellishments we have also implemented.

@@

For $p(\beta | \shat)$ we assume that the $\beta_j$ are independent from a unimodal distribution $g$.
This unimodal assumption (UA) is a key assumption that distinguishes our approach from previous EB approaches to FDR analysis.
A simple way to implement the UA is to assume that $g$ is
a mixture of a point mass at 0 and a mixture of {\it zero-mean} normal distributions:
\begin{align} \label{eqn:beta}
p(\beta | \shat, \pi) & = \prod_j g(\beta_j; \pi), \\   
g(\cdot; \pi) & = \pi_0 \delta_0(\cdot) + \sum_{k=1}^K \pi_k N(\cdot; 0, \sigma_k^2), \label{eqn:mixnorm}
\end{align}
where $N(\cdot; \mu, \sigma^2)$ denotes the density of the normal distribution with mean $\mu$ and variance $\sigma^2$.
Here the mixture proportions $\pi=(\pi_0,\dots,\pi_K)$ are hyperparameters, which are non-negative and sum to one, and are to be estimated,
while the mixture component standard deviations $\sigma_1,\dots,\sigma_K$ 
represent a large and dense grid of {\it fixed} positive numbers spanning a range from very small to very big (so $K$ is fixed and large). 
(We encourate the reader to think of this grid as becoming infinitely large and dense, as a non-parametric limit,
although of course in practice we use a finite grid -- see Implementation Details.)

@@

This simple model features both the key ideas we want to emphasise in this paper: the UA is encapsulated in (\ref{eqn:mixnorm}) while
the different measurement precision of different observations is encapsulated in the likelihood (\ref{eqn:normlik}) -- specifically, observations
with larger standard error will have a flatter likelihood, and therefore have less impact on inference.
However, this simple model also has several additional assumptions that can be relaxed. Specifically,
\begin{enumerate}
\item  The use of a mixture of zero-mean normals (\ref{eqn:mixnorm}) also implies that $g$ is symmetric about 0; more flexibility can be obtained by replacing the mixture of normals with mixtures of uniforms [see (\ref{eqn:g-general})].
\item The model (\ref{eqn:beta}) assumes that the effects are identically distributed, independent of their standard errors $\shat$.
We can relax this to allow for a relationship between these quantities [see (\ref{eqn:beta-alpha})].
\item The likelihood (\ref{eqn:normlik}) effectively assumes that the number of observations used to compute $\bhat_j,\shat_j$ are sufficiently large to justify a normal approximation. We can generalize this likelihood using a $t$ likelihood [see (\ref{eqn:tlik})].
\end{enumerate}
These embellishments are detailed in Detailed Methods.
Of course there remain limitations that are harder to relax, most notably the independence and conditional independence assumptions encapsulated in our model
(which are also made by most existing EB approaches to this problem). Correlations among tests certainly arise in practice, either due to genuine correlations
in the system of study, or due to unmeasured confounders, and their potential to impact results of an FDR analysis is important to consider
whatever analysis methods are used: see \cite{efron2007correlation,leek:2007} for relevant discussion.

@@

The usual EB approach to fitting this model would involve two simple steps:
\begin{enumerate}
\item Estimate the hyperparameters $\pi$ by maximizing the likelihood $L(\pi)$, given by (\ref{eqn:marginallik}), yielding $\hat{\pi} := \arg \max L(\pi)$.
\item Compute quantities of interest from the conditional distributions $p(\beta_j | \bhat, \shat, \hat{\pi})$. For example, the evidence
against the null hypothesis $\beta_j=0$ can be summarized by $p(\beta_j \neq 0 | | \bhat, \shat,\hat{\pi})$.
\end{enumerate}
Both steps 1 and 2 are very straightforward: $\hat{\pi}$ can be obtained using a simple EM algorithm \cite{dempster77}, and the conditional distributions $p(\beta_j | \bhat_j, \shat_j,\hat{\pi})$ are analytically available, each a mixture of a point mass on zero and $K$ normal distributions.
(The simplicity of the EM algorithm in step 1 is due to our use of a fixed grid for $\sigma_k$ in (\ref{eqn:mixnorm}), instead of estimating $\sigma_k$,
which may seem more natural but is not straightforward when $\shat_j$ varies among $j$. This simple device may be useful in other applications.)

Here we slightly modify this usual procedure: instead of obtaining $\hat\pi$ by maximizing the likelihood, we maximise a penalized
likelihood [see (\ref{eqn:penalty})], where the penalty encourages $\hat\pi_0$ to be as big as possible whilst remaining consistent with the observed data. 
We introduce this penalty because in FDR appllications it is considered desirable to avoid underestimating $\pi_0$ so as to avoid underestimating the FDR.

@@

As our notation suggests, $\lfsr_j$ is intended to be compared and contrasted with $\lfdr_j$: whereas small values of $\lfdr_j$ indicate that we can be {\it confident that $\beta_j$ is non-zero}, 
small values of $\lfsr_j$ indicate that we can be {\it confident in the sign of $\beta_j$}. 
Of coure, being confident in the sign of an effect logically implies that we are confident it is non-zero, and
this is reflected in the fact that $\lfsr_j \geq \lfdr_j$ 
(this follows from the definition because both the events $\beta_j \geq 0$
and $\beta_j \leq 0$ in (\ref{eqn:lfsr}) include the event $\beta_j=0$).
In this sense, as a measure of ``significance", $\lfsr$ is more conservative than $\lfdr$. More importantly, as we illustrate in Results,
$\lfsr$ can be substantially more robust to modelling assumptions than $\lfdr$.

@@

Given that the UA and ZA are so different, it seems worth discussing why we generally favor the UA. 
Although the UA will not apply to all situations, we believe that it will often be reasonable, especially in FDR-related contexts
that have traditionally focussed on rejecting the null hypotheses $\beta_j=0$. This is because if ``$\beta_j=0$" is a plausible null hypothesis,  
it seems reasonable to expect that ``$\beta_j$ very near 0" is also plausible. Further, it seems reasonable to expect that larger effects become
decreasingly plausible, and so the distribution of the effects will be unimodal about 0. To paraphrase Tukey, ``All we know about the world teaches us that large effects are rare, whereas small effects abound."
We emphasise that the UA relates to the distribution of {\it all} effects, and not only the {\it detectable} effects (i.e.~those that are significantly different from zero). It is very likely that the distribution of {\it detectable} non-zero effects will be multimodal, with one mode for detectable positive effects and another for detectable negative effects, and the UA does not contradict this.

@@

In further support of the UA for FDR applications, we note that almost all analogous work in sparse regression models make the UA for the regression coefficents - 
common choices of uni-modal distribution being the spike and slab, Laplace, $t$, normal-gamma, normal-inverse-gamma, or horseshoe priors \cite{carvalho2010horseshoe}.
These are all less flexible than the approach we take here, which provides for general uni-modal distributions, and 
it may be fruitful to apply our methods to the regression context; indeed see \cite{moser:2015} for work in this vein. 
The UA assumption on regression coefficients is directly analagous to our UA here, and so its
widespread use in the regression context supports its use here.

@@

Finally, the UA also has a considerable practical benefit: it yields simple algorithms that are both computationally
and statistically stable. We illustrate these features in Results.

@@

There is also a very considerable literature that does not directly focus on the FDR problem, but which involves similar ideas and methods. 
 Among these, a paper about deconvolution \cite{cordy1997deconvolution} is most similar, methodologically, to our work here:
indeed, this paper includes all the elements of our approach outlined above, except for the point mass on 0 and corresponding penalty term.
This said, the focus is very different: \cite{cordy1997deconvolution} focuses entirely on estimating $g$, whereas our primary focus is on estimating $\beta_j$.
Also, they provide no software implementation.  More generally, the related literature is too large to review comprehensively, but relevant key-words include ``empirical bayes", ``shrinkage", ``deconvolution", ``semi-parametric", ``shape-constrained", and ``heteroskedastic". Some pointers to recent papers in which other relevant
citations can be found include \cite{xie2012sure, sarkar:2014, koenker2014convex}. Much of the literature focusses on the homoskedastic case (i.e. $\shat_j$ all equal) whereas we allow for heteroskedasticity. And much of the recent shrinkage-oriented literature focuses only on point estimation of $\beta_j$, whereas for FDR-related applications measures of uncertainty are essential. Several recent papers consider more flexible non-parametric assumptions on 
$g$ than the UA assumption we make here. In particular, \cite{jiang2009general,koenker2014convex} consider the unconstrained non-parametric maximum likelihood
estimate (NPMLE) for $g$. These methods may provide alternatives to our approach in settings where the UA assumption is considered too restrictive. However, the  NPMLE for $g$ is a discrete distribution, which will induce a discrete posterior distribution on $\beta_j$, and so although the NPMLE
may perform well for point estimation, it seems possible it will not adequately reflect uncertainty in $\beta_j$, and some regularization on $g$ may be necessary.
Indeed, one way of thinking about the UA is as a way to regularize $g$.

@@

The illustration in Figure \ref{fig:ZA} suggests that the UA will produce smaller estimates of $\pi_0$ than the ZA.
Consequently \ashr will estimate smaller $\lfdr$s and FDRs than existing methods that make the ZA. 
This is desirable, provided that these estimates remain conservative: that is,
provided that $\pi_0$ does not underestimate the true $\pi_0$ and $\lfdr$ does not underestimate the true $\lfdr$.
The penalty term (\ref{eqn:penalty}) aims to ensure this conservative behaviour. To check its effectiveness
we performed simulations under various alternative scenarios (i.e. various distributions for the non-zero effects, which we denote $g_1$), and values
for $\pi_0$. The alternative distributions are shown in Figure \ref{fig:altdens}, with details in Table \ref{table:scenarios}.
They range from a ``spiky" distribution -- where many non-zero $\beta$ are
too close to  zero to be reliably detected, making reliable estimation of $\pi_0$ essentially impossible -- to a much
flatter distribution, which is a normal distribution with large variance (``big-normal") -- where most non-zero $\beta$ are easily detected
making reliable estimation of $\pi_0$ easier. We also include one asymmetric distribution (``skew"), and one clearly bimodal distribution (``bimodal"),
which, although we view as generally unrealistic, we include to assess robustness of \ashr~to deviations from the UA.

@@

The results above show that \ashr can improve on existing methods in producing smaller, more accurate, 
estimates of $\pi_0$, which will lead to more accurate estimates of FDR.
Nonetheless, in many scenarios \ashr continues
to substantially over-estimate $\pi_0$ (see the ``spiky" scenario for example). 
This is because these scenarios include 
an appreciable fraction of ``small non-null effects" that are essentially indistinguishable from 0, making accurate
estimation of $\pi_0$ impossible. Put another way, and as is well known, $\pi_0$ is not identifiable:
 the data can effectively provide an upper bound on plausible values of $\pi_0$,
but not a lower bound (because the data cannot rule out that everything is non-null, but with miniscule effects).
To obtain conservative behaviour we must estimate $\pi_0$ by this upper bound, which can
be substantially larger than the true value.

@@

The key point we want to make here is estimation of $\pi_0$, and the accompanying identifiability issues,
 become substantially less troublesome if we use the local false sign rate $\lfsr$ (\ref{eqn:lfsr}), rather than $\lfdr$, to measure significance. 
 This is essentially because $\lfsr$ is less sensitive to the estimate of $\pi_0$.
To illustrate, Figure \ref{fig:lfsr} compares the estimated $\lfsr$ from ash.n with the true value: although the estimated $\lfsr$ continue to
be conservative, overestimating the truth, the overestimation is substantially less pronounced than for the $\lfdr$, especially for
the ``spiky" scenario. Further, in the bi-modal scenario, the anti-conservative behaviour is less pronounced in $\lfsr$ than $\lfdr$.

@@

\subsubsection*{Numerical Stability}

The EM algorithm, which we use here to fit our model, is notorious for convergence to local optima. 
However, in this case, over hundreds of applications of the procedure, we observed no obvious serious problems 
caused by such behaviour. To quantify this, we ran \ashr 10 times on each of the 600 simulated datasets above using a random initialization for $\pi$,
in addition running it using our default initialization procedure (see Implementation details). We then compared the largest
log-likelihood achieved across all 11 runs with the log-likelihood achieved by the default run.
When using a mixture of normals (ash.n) the results were extremely stable: 96\% showed a negligible log-likelihood difference ($< 0.02$), 
and the largest difference was 0.8. When using mixtures of uniforms (ash.u,ash.hu) results were slightly less stable: 89\% showed a negligible log-likelihood difference ($<0.02$),
and 6\% of runs showed an appreciable log-likelihood difference ($>1$), with the largest difference being 5.0. However, perhaps suprisingly, 
even for this largest difference results from the default run (e.g. the $\lfsr$ values, and the posterior means) were in other ways virtually indistinguishable from the results from the run with the highest log-likelihood. See \url{http://github.com/stephens999/ash/blob/master/dsc-robust/summarize_dsc_robust.rmd} for further details.

@@

The ability of the EB approach to provide valid ``post-selection" interval estimates is extremely attractive in principle.
But its usefulness in practice
depends on reliably estimating the distribution $g$. Estimating $g$ is a ``deconvolution problem",
which are notoriously difficult in general. Indeed, Efron emphasises
the difficulties of implementing a stable general algorithm, noting in his rejoinder
``the effort foundered on practical difficulties involving the perils of deconvolution... Maybe I am trying
to be overly nonparametric ... but it is hard to imagine a
generally satisfactory parametric formulation..." (\cite{efron2008microarrays} rejoinder, p46).
Our key point here is that the UA greatly simplifies the deconvolution problem.
While not meeting Efron's desire for an entirely general nonparametric approach, we believe 
that the UA can handle many cases of practical interest.

To illustrate this, Figure \ref{fig:egcdf} compares the
estimated $g$ from \ashr  with that from \mixfdr which does not make the UA 
(and which models $g$ as a mixture of $J$ normal distributions, with $J=3$ by default).
The greater reliability of estimates afforded
by the UA is immediately apparent. In particular the estimated cdf from \mixfdr often has an almost-vertical
segment at some non-zero location, indicative of a concentration of density in the estimated $g$ at that location. 
The UA prevents this kind of ``irregular" behaviour, effectively requiring $g$ to be somewhat smooth.
While the UA is not the only way to achieve this, we find it an attractive, simple and effective approach.

@@

Another consequence of accounting for differences in measurement precision is that \ashr may re-order the significance of the observations compared
 with the original $p$ values or $z$ scores. This is illustrated, using the same simulation as above, in Figure \ref{fig:lfsr_pval} (left panel).
 We see that poor precision measurements are assigned a higher $\lfsr$ than good precision measuments that have the same $p$ value.
 The intuition is that, due to their poor precision, these measurements contain very little information about the sign of the effects (or indeed any other aspect of the effects),
 and so the $\lfsr$ for these poor-precision measurements is always high.

>>>>

We introduce a novel Empirical Bayes approach for performing large-scale hypothesis testing, including  
estimating False Discovery Rates (FDRs), and estimating effect sizes. Compared with
existing commonly-used approaches to FDR analysis, the method has two key differences. First, it
assumes that the distribution of the actual (unobserved) effects being tested is unimodal, with a mode at 0.
This ``unimodal assumption" (UA), which is common in other related contexts, but very different from assumptions usually made
in FDR analyses, yields more accurate estimates of FDR than existing methods, provided the UA holds.
It also facilitates efficient and robust computation because estimating the unimodal distribution involves solving a simple convex optimization problem.
Second, the method takes as its input two numbers for each test (an effect size estimate, and corresponding standard error),
rather than the one number usually used ($p$ value, or $z$ score). When available, using two numbers instead of one allows 
for better accounting of variations in measurement precision across tests. It also facilitates the estimation of actual 
effect sizes, and our approach provides interval estimates (credible regions) for each effect in addition to measures of significance.
To provide a bridge between interval estimates and significance measures we introduce the term ``local false sign rate"
to refer to the probability of getting the sign of an effect wrong, and argue that it is a superior
measure of significance than the local FDR because it is both more generally applicable, and
can be more robustly estimated. Our methods are implemented in an R package {\tt ashr}
available from \url{http://github.com/stephens999/ashr}.

@@

In addition to these two new ideas, we highlight a third idea that is old, but which remains under-used in practice:
the idea that it may be preferable to focus on estimation rather than on testing.
In principle, Bayesian approaches can naturally unify testing and estimation into a single framework -- testing is
simply estimation with some positive prior probability that the effect is exactly zero.
However, despite ongoing interest in this area from both frequentist \cite{benjamini2005false} and Bayesian \cite{zhao2012empirical,gelman2012we} 
perspectives, in practice large-scale studies that assess many effects almost invariably focus on testing significance and
controlling the FDR, and not on estimation. To help provide a bridge between FDR and estimation we introduce the term
``local false sign rate" (lfsr), which is analogous to the ``local false discovery rate" (\lfdr) \cite{efron2008microarrays}, but which measures confidence  
in the {\it sign} of each effect rather than confidence in each effect being non-zero. We show that in some settings, particularly those with many discoveries, 
the $\lfsr$ and $\lfdr$ can be quite different, and emphasize benefits of the $\lfsr$, particularly its increased robustness to modeling assumptions.

@@

Our methods are implemented in an R package, \ashr (for {\bf a}daptive {\bf sh}rinkage in {\bf R}), available at \url{http://github.com/stephens999/ashr}.
(The names comes from the fact that EB methods in general -- and, due to the UA, our EB method in particular -- perform shrinkage estimation,
and the shrinkage is adaptive to both the amount of signal in the data and the measurement precision of each observation. 
This will be discussed further in Xing and Stephens (in preparation).)

@@

% Here we consider one setting in which FDR-based methods are widely used:
%an experimenter has measured a large numbers of ``effects", each with an associated
%measurement precision (standard error), 
%and the goal is to identify which of the effects we can declare to be non-zero, with some prescribed level of confidence.
%Although the usual focus of FDR-based methods is on distinguishing zero and non-zero effects,
%here we also focus on providing estimates -- both point estimates and interval estimates -- for these effects.
%This setting arises commonly in many areas of statistics, and particularly in genomics applications.
%For example, in genomics
%a common goal is to identify ``differentially-expressed genes" -- that is, genes
%whose mean expression (activity) level differs in two conditions. Here the ``effect" of interest is the difference in (log) 
%mean expression level between the two conditions, often referred to as the ``log-fold change". 
Here we describe the simplest version of the method, and briefly discuss embellishments we have also implemented.

@@

For $p(\beta | \shat)$ we assume that the $\beta_j$ are independent from a unimodal distribution $g$.
This unimodal assumption (UA) is a key assumption that distinguishes our approach from previous EB approaches to FDR analysis.
A simple way to implement the UA is to assume that $g$ is
a mixture of a point mass at 0 and a mixture of {\it zero-mean} normal distributions:
\begin{align} \label{eqn:beta}
p(\beta | \shat, \pi) & = \prod_j g(\beta_j; \pi), \\   
g(\cdot; \pi) & = \pi_0 \delta_0(\cdot) + \sum_{k=1}^K \pi_k N(\cdot; 0, \sigma_k^2), \label{eqn:mixnorm}
\end{align}
where $N(\cdot; \mu, \sigma^2)$ denotes the density of the normal distribution with mean $\mu$ and variance $\sigma^2$.
Here the mixture proportions $\pi=(\pi_0,\dots,\pi_K)$ are hyper-parameters, which are non-negative and sum to one, and are to be estimated,
while the mixture component standard deviations $\sigma_1,\dots,\sigma_K$ 
represent a large and dense grid of {\it fixed} positive numbers spanning a range from very small to very big (so $K$ is fixed and large). 
(We encourage the reader to think of this grid as becoming infinitely large and dense, as a non-parametric limit,
although of course in practice we use a finite grid -- see Implementation Details.)

@@

This simple model features both the key ideas we want to emphasize in this paper: the UA is encapsulated in (\ref{eqn:mixnorm}) while
the different measurement precision of different observations is encapsulated in the likelihood (\ref{eqn:normlik}) -- specifically, observations
with larger standard error will have a flatter likelihood, and therefore have less impact on inference.
However, this simple model also has several additional assumptions that can be relaxed. Specifically,
\begin{enumerate}
\item  The use of a mixture of zero-mean normals (\ref{eqn:mixnorm}) implies that $g$ is symmetric about 0.
More flexibility can be obtained by replacing the mixture of normals with mixtures of uniforms [see equation (\ref{eqn:g-general})]; indeed this 
can allow $g$ to approximate {\it any} unimodal distribution. 
\item The model (\ref{eqn:beta}) assumes that the effects are identically distributed, independent of their standard errors $\shat$.
We can relax this to allow for a relationship between these quantities [see (\ref{eqn:beta-alpha})].
\item The likelihood (\ref{eqn:normlik}) effectively assumes that the number of observations used to compute $\bhat_j,\shat_j$ are sufficiently large to justify a normal approximation. We can generalize this likelihood using a $t$ likelihood [see (\ref{eqn:tlik})].
\end{enumerate}
These embellishments are detailed in Detailed Methods.
Of course there remain limitations that are harder to relax, most notably the independence and conditional independence assumptions encapsulated in our model
(which are also made by most existing EB approaches to this problem). Correlations among tests certainly arise in practice, either due to genuine correlations
in the system of study, or due to unmeasured confounders, and their potential to impact results of an FDR analysis is important to consider
whatever analysis methods are used: see \cite{efron2007correlation,leek:2007} for relevant discussion.

@@

The usual EB approach to fitting this model would involve two simple steps:
\begin{enumerate}
\item Estimate the hyper-parameters $\pi$ by maximizing the likelihood $L(\pi)$, given by (\ref{eqn:marginallik}), yielding $\hat{\pi} := \arg \max L(\pi)$.
\item Compute quantities of interest from the conditional distributions $p(\beta_j | \bhat, \shat, \hat{\pi})$. For example, the evidence
against the null hypothesis $\beta_j=0$ can be summarized by $p(\beta_j \neq 0 | | \bhat, \shat,\hat{\pi})$.
\end{enumerate}
Both steps 1 and 2 are very straightforward. Step 1 is a convex optimization problem \cite{}, and can be solved very quickly using interior point methods \cite{boyd2004convex,koenker2013convex}. And the conditional distributions $p(\beta_j | \bhat_j, \shat_j,\hat{\pi})$ in Step 2 are analytically available, each a mixture of a point mass on zero and $K$ normal distributions.
(The simplicity of step 1 is due to our use of a fixed grid for $\sigma_k$ in (\ref{eqn:mixnorm}), instead of estimating $\sigma_k$,
which may seem more natural but is not straightforward when $\shat_j$ varies among $j$. This simple device may be useful in other applications.)

Here we slightly modify this usual procedure: instead of obtaining $\hat\pi$ by maximizing the likelihood, we maximize a penalized
likelihood [see (\ref{eqn:penalty})], where the penalty encourages $\hat\pi_0$ to be as big as possible whilst remaining consistent with the observed data. 
We introduce this penalty because in FDR applications it is considered desirable to avoid underestimating $\pi_0$ so as to avoid underestimating the FDR.

@@

As our notation suggests, $\lfsr_j$ is intended to be compared and contrasted with $\lfdr_j$: whereas small values of $\lfdr_j$ indicate that we can be {\it confident that $\beta_j$ is non-zero}, 
small values of $\lfsr_j$ indicate that we can be {\it confident in the sign of $\beta_j$}. 
Of course, being confident in the sign of an effect logically implies that we are confident it is non-zero, and
this is reflected in the fact that $\lfsr_j \geq \lfdr_j$ 
(this follows from the definition because both the events $\beta_j \geq 0$
and $\beta_j \leq 0$ in (\ref{eqn:lfsr}) include the event $\beta_j=0$).
In this sense, as a measure of ``significance", $\lfsr$ is more conservative than $\lfdr$. More importantly, as we illustrate in Results,
$\lfsr$ can be substantially more robust to modeling assumptions than $\lfdr$.

@@

Given that the UA and ZA are so different, it seems worth discussing why we generally favor the UA. 
Although the UA will not apply to all situations, we believe that it will often be reasonable, especially in FDR-related contexts
that have traditionally focussed on rejecting the null hypotheses $\beta_j=0$. This is because if ``$\beta_j=0$" is a plausible null hypothesis,  
it seems reasonable to expect that ``$\beta_j$ very near 0" is also plausible. Further, it seems reasonable to expect that larger effects become
decreasingly plausible, and so the distribution of the effects will be unimodal about 0. To paraphrase Tukey, ``All we know about the world teaches us that large effects are rare, whereas small effects abound."
We emphasize that the UA relates to the distribution of {\it all} effects, and not only the {\it detectable} effects (i.e.~those that are significantly different from zero). It is very likely that the distribution of {\it detectable} non-zero effects will be multimodal, with one mode for detectable positive effects and another for detectable negative effects, and the UA does not contradict this.

@@

In further support of the UA for FDR applications, we note that almost all analogous work in sparse regression models make the UA for the regression coefficients -- 
common choices of uni-modal distribution being the spike and slab, Laplace, $t$, normal-gamma, normal-inverse-gamma, or horseshoe priors \cite{carvalho2010horseshoe}.
These are all less flexible than the approach we take here, which provides for general uni-modal distributions, and 
it may be fruitful to apply our methods to the regression context; indeed see \cite{moser:2015} for work in this vein. 
The UA assumption on regression coefficients is directly analagous to our UA here, and so its
widespread use in the regression context supports its use here.

@@

Finally, the UA also has a considerable practical benefit: it yields simple algorithms that are both computationally
and statistically stable (see Results).

@@

There is also a very considerable literature that does not directly focus on the FDR problem, but which involves similar ideas and methods. 
 Among these, a paper about deconvolution \cite{cordy1997deconvolution} is most similar, methodologically, to our work here:
indeed, this paper includes all the elements of our approach outlined above, except for the point mass on 0 and corresponding penalty term.
This said, the focus is very different: \cite{cordy1997deconvolution} focuses entirely on estimating $g$, whereas our primary focus is on estimating $\beta_j$.
Also, they provide no software implementation.  More generally, the related literature is too large to review comprehensively, but relevant key-words include ``empirical bayes", ``shrinkage", ``deconvolution", ``semi-parametric", ``shape-constrained", and ``heteroskedastic". Some pointers to recent papers in which other relevant
citations can be found include \cite{xie2012sure, sarkar:2014, koenker2014convex}. Much of the literature focusses on the homoskedastic case (i.e. $\shat_j$ all equal) whereas we allow for heteroskedasticity. And much of the recent shrinkage-oriented literature focuses only on point estimation of $\beta_j$, whereas for FDR-related applications measures of uncertainty are essential. Several recent papers consider more flexible non-parametric assumptions on 
$g$ than the UA assumption we make here. In particular, \cite{jiang2009general,koenker2014convex} consider the unconstrained non-parametric maximum likelihood
estimate (NPMLE) for $g$. These methods may provide alternatives to our approach in settings where the UA assumption is considered too restrictive. However, the  NPMLE for $g$ is a discrete distribution, which will induce a discrete posterior distribution on $\beta_j$, and so although the NPMLE
may perform well for point estimation, it may not adequately reflect uncertainty in $\beta_j$, and some regularization on $g$ may be necessary.
Indeed, one way of thinking about the UA is as a way to regularize $g$.

@@

The illustration in Figure \ref{fig:ZA} suggests that the UA will produce smaller estimates of $\pi_0$ than the ZA.
Consequently \ashr will estimate smaller $\lfdr$s and FDRs than existing methods that make the ZA. 
This is desirable, provided that these estimates remain conservative: that is,
provided that $\pi_0$ does not underestimate the true $\pi_0$ and $\lfdr$ does not underestimate the true $\lfdr$.
The penalty term (\ref{eqn:penalty}) aims to ensure this conservative behavior. To check its effectiveness
we performed simulations under various alternative scenarios (i.e. various distributions for the non-zero effects, which we denote $g_1$), and values
for $\pi_0$. The alternative distributions are shown in Figure \ref{fig:altdens}, with details in Table \ref{table:scenarios}.
They range from a ``spiky" distribution -- where many non-zero $\beta$ are
too close to  zero to be reliably detected, making reliable estimation of $\pi_0$ essentially impossible -- to a much
flatter distribution, which is a normal distribution with large variance (``big-normal") -- where most non-zero $\beta$ are easily detected
making reliable estimation of $\pi_0$ easier. We also include one asymmetric distribution (``skew"), and one clearly bimodal distribution (``bimodal"),
which, although we view as generally unrealistic, we include to assess robustness of \ashr~to deviations from the UA.

@@

The results above show that \ashr can improve on existing methods in producing smaller, more accurate, 
estimates of $\pi_0$, which will lead to more accurate estimates of FDR.
Nonetheless, in many scenarios \ashr continues
to substantially over-estimate $\pi_0$ (see the ``spiky" scenario for example). 
This is because these scenarios include 
an appreciable fraction of ``small non-null effects" that are essentially indistinguishable from 0, making accurate
estimation of $\pi_0$ impossible. Put another way, and as is well known, $\pi_0$ is not identifiable:
 the data can effectively provide an upper bound on plausible values of $\pi_0$,
but not a lower bound (because the data cannot rule out that everything is non-null, but with minuscule effects).
To obtain conservative behavior we must estimate $\pi_0$ by this upper bound, which can
be substantially larger than the true value.

@@

The key point we want to make here is estimation of $\pi_0$, and the accompanying identifiability issues,
 become substantially less troublesome if we use the local false sign rate $\lfsr$ (\ref{eqn:lfsr}), rather than $\lfdr$, to measure significance. 
 This is essentially because $\lfsr$ is less sensitive to the estimate of $\pi_0$.
To illustrate, Figure \ref{fig:lfsr} compares the estimated $\lfsr$ from ash.n with the true value: although the estimated $\lfsr$ continue to
be conservative, overestimating the truth, the overestimation is substantially less pronounced than for the $\lfdr$, especially for
the ``spiky" scenario. Further, in the bi-modal scenario, the anti-conservative behavior is less pronounced in $\lfsr$ than $\lfdr$.

@@

@@

The ability of the EB approach to provide valid ``post-selection" interval estimates is extremely attractive in principle.
But its usefulness in practice
depends on reliably estimating the distribution $g$. Estimating $g$ is a ``deconvolution problem",
which are notoriously difficult in general. Indeed, Efron emphasizes
the difficulties of implementing a stable general algorithm, noting in his rejoinder
``the effort foundered on practical difficulties involving the perils of deconvolution... Maybe I am trying
to be overly nonparametric ... but it is hard to imagine a
generally satisfactory parametric formulation..." (\cite{efron2008microarrays} rejoinder, p46).
Our key point here is that the UA greatly simplifies the deconvolution problem.
While not meeting Efron's desire for an entirely general nonparametric approach, we believe 
that the UA can handle many cases of practical interest.

To illustrate this, Figure \ref{fig:egcdf} compares the
estimated $g$ from \ashr  with that from \mixfdr which does not make the UA 
(and which models $g$ as a mixture of $J$ normal distributions, with $J=3$ by default).
The greater reliability of estimates afforded
by the UA is immediately apparent. In particular the estimated cdf from \mixfdr often has an almost-vertical
segment at some non-zero location, indicative of a concentration of density in the estimated $g$ at that location. 
The UA prevents this kind of ``irregular" behavior, effectively requiring $g$ to be somewhat smooth.
While the UA is not the only way to achieve this, we find it an attractive, simple and effective approach.

@@

Another consequence of accounting for differences in measurement precision is that \ashr may re-order the significance of the observations compared
 with the original $p$ values or $z$ scores. This is illustrated, using the same simulation as above, in Figure \ref{fig:lfsr_pval} (left panel).
 We see that poor precision measurements are assigned a higher $\lfsr$ than good precision measurements that have the same $p$ value.
 The intuition is that, due to their poor precision, these measurements contain very little information about the sign of the effects (or indeed any other aspect of the effects),
 and so the $\lfsr$ for these poor-precision measurements is always high.
